How do domestic GDP growth, global economic conditions, and financial crises impact the export growth rate in different countries?

### 2024-04-19 paper/paper.qmd
new Commit

>>>>

```{r}
ggplot(data, aes(x=GDPgrAbroad, y=trade_count)) +
  geom_point(aes(color=factor(BANK)), alpha=0.6) +  # Color points by BANK status
  labs(x = "Foreign GDP Growth Rate", y = "Trade Count", color = "Banking Crisis") +
  theme_minimal() +
  geom_smooth(method="lm", se=FALSE) 
```

```{r}
ggplot(data, aes(x=factor(BANK), y=trade_count, fill=factor(BANK))) +
  geom_bar(stat="summary", fun=mean, position=position_dodge(), width=0.7) +
  labs(x = "Banking Crisis (0 = No, 1 = Yes)", y = "Average Trade Count", fill = "Banking Crisis") +
  theme_minimal()
```

```{r}
data_JPN_usa <- data %>%
  filter(exporter %in% c("JPN", "USA", "ITA"))

ggplot(data_JPN_usa, aes(x=factor(BANK), y=trade_count, fill=exporter)) +
  geom_bar(stat="summary", fun=mean, position=position_dodge(), width=0.7) +
  labs(x = "Banking Crisis (0 = No, 1 = Yes)", y = "Average Trade Count", title = "Banking Crisis Impact on Trade") +
  scale_fill_manual(values=c("JPN"="blue", "USA"="red", "ITA"="green")) +
  theme_minimal()
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-model_summary
#| tbl-cap: Model Summary for Poisson and Negative Binomial Models

# Load the saved models
stan_poisson_model <- readRDS("/cloud/project/models/first_model.rds")

stan_nb_model <- readRDS("/cloud/project/models/second_model.rds")

# Generate model summaries
model_summary_poisson <- summary(stan_poisson_model)
model_summary_nb <- summary(stan_nb_model)

# Combine summaries into a table
model_summary_table <- rbind(
  "Poisson Model" = coef(model_summary_poisson),
  "Negative Binomial Model" = coef(model_summary_nb)
)

# Print the table
print(model_summary_table)
